Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
typo

In order to exploit the present approach full potential, a dynamical plant that can
present physical components must be considered.  However, a discrete plant
model can also demonstrate some benefits of the present approach, which
considers FWL effects in the digital controller implementation.  In
particular, a classical cruise control example is extracted from the
literature~\cite{Astrom08}, where the discrete plant model (with time step
of $0.2$s) is represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

@@

\subsubsection{Program synthesis for the illustrative example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

>>>>

In order to exploit the full potential of the present approach, a
dynamical plant that can present physical components must be
considered.  However, a discrete plant model can also demonstrate some
benefits of the present approach, which considers FWL effects in the
digital controller implementation.  In particular, a classical cruise
control example is extracted from the literature~\cite{Astrom08},
where the discrete plant model (with time step of $0.2$s) is
represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

@@

\subsubsection{Program synthesis for the illustrative example}
We will illustrate our synthesis approach on the running example
described in the previous section. 
%in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
